Abstract Plots

### 2021-08-19 Abstract.Rmd
Updated fig 2a and package versions

---
title: "Abstract Plots"
author: "Audrey Mitchell"
date: "7/21/2021"
output: html_document
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(NMF)
library(MutationalPatterns)
library(tidyverse)
library(ggrepel)
library(ROCR)
library(gridExtra)
source("bayes_function.R")
source("get_classification_df.R")
source("simulation.R")
```

@@

```{r}
#Create Signature 4 Sample
sig4.500 <- create_signature_sample_vector(signature.4.mat, 500)
sig4.profile <- vector_to_matrix(sig4.500)

@@

plot(MMR.perf, print.cutoffs.at=0.5, text.adj=c(-0.2,1.7),
     main = "ROC curve of classifier", lty = 2) #ROC
plot(tob.perf, print.cutoffs.at=0.5, text.adj=c(-0.2,1.7), 
     add = TRUE, lty = 3)
abline(a=0, b= 1)
legend("bottomright", c("Signature 6 with FFPE noise", "Signature 4 with FFPE noise"),
       lty = 2:3)

@@

# Mutational load performance characteristics

## Mutational load predictions

```{r}
step_load = seq(50, 1000, by = 50)
MMR.probabilities <- vector(mode = "list", length = length(step))
MMR.truth <- vector(mode = "list", length = length(step))

for (x in 1:length(step)){
  sample.ffpe <- create_signature_sample_vector(ffpe.sig, step[x]/2)
  ffpe.truth <- rep("FFPE", step[x]/2)
  sample.sig6 <- create_signature_sample_vector(cosmic.sig6, step[x]/2)
  sig6.truth <- rep("MMR", step[x]/2)
  test <- get_classification_df(list(sample.sig6, sample.ffpe), c("MMR","FFPE"),
                                list(cosmic.sig6, ffpe.sig))
  classification <- test %>%
    mutate(trueBinary = ifelse(truth == "MMR",1,0))

  MMR.probabilities[[x]] <- classification$MMR
  MMR.truth[[x]] <- classification$trueBinary
}
```

```{r}
tob.probabilities <- vector(mode = "list", length = length(step))
tob.truth <- vector(mode = "list", length = length(step))

for (x in 1:length(step)){
  sample.ffpe <- create_signature_sample_vector(ffpe.sig, step[x]/2)
  ffpe.truth <- rep("FFPE", step[x]/2)
  sample.sig4 <- create_signature_sample_vector(cosmic.sig4, step[x]/2)
  sig4.truth <- rep("tob", step[x]/2)
  test <- get_classification_df(list(sample.sig4, sample.ffpe), c("Tobacco","FFPE"),
                                list(cosmic.sig4, ffpe.sig))
  classification <- test %>%
    mutate(trueBinary = ifelse(truth == "Tobacco",1,0))

  tob.probabilities[[x]] <- classification$Tobacco
  tob.truth[[x]] <- classification$trueBinary
}
```

```{r}
load.MMR <- prediction(MMR.probabilities, MMR.truth)
load.tob <- prediction(tob.probabilities, tob.truth)
```

```{r}
load.sens.MMR.vec = evaluate_perf(100, length(step_load), load.MMR, "sens")
load.sens.tob.vec = evaluate_perf(100, length(step_load), load.tob, "sens")
```

```{r}
#plot(step, load.sens.MMR.vec, ylim = c(0,1))
sensitivity = append(load.sens.MMR.vec, load.sens.tob.vec)
signature.sens = append(rep("MMR", length(load.sens.MMR.vec)),
                        rep("Tobacco", length(load.sens.tob.vec)))
dilution = append(step, step)
sens.df <- data.frame(dilution, sensitivity, signature.sens)

ggplot(data = sens.df, mapping = aes(x = dilution, 
                                     y = sensitivity, 
                                     color = signature.sens)) +
  geom_point() +
  geom_smooth() +
  labs(title = "Sensitivity as a function of mutational load",
       x = "Number of mutations in each sample",
       y = "Sensitivity value",
       color = "True signal") +
  coord_cartesian(ylim = c(0,1))
```

```{r}
load.spec.MMR.vec = evaluate_perf(100, length(step.load), load.MMR, "spec")
load.spec.tob.vec = evaluate_perf(100, length(step.load), load.tob, "spec")
```

```{r}
#plot(step, load.spec.MMR.vec, ylim = c(0,1))

specificity = append(load.spec.MMR.vec, load.spec.tob.vec)
signature.spec = append(rep("MMR", length(load.spec.MMR.vec)),
                        rep("Tobacco", length(load.spec.tob.vec)))
dilution = append(step, step)
spec.df <- data.frame(dilution, specificity, signature.spec)

ggplot(data = spec.df, mapping = aes(x = dilution, 
                                     y = specificity, 
                                     color = signature.spec)) +
  geom_point() +
  geom_smooth() +
  labs(title = "Specificity as a function of mutational load",
       x = "Number of mutations in each sample",
       y = "Specificity value",
       color = "True signal") +
  coord_cartesian(ylim = c(0,1))
```

>>>>

---
title: "Abstract Plots"
author: "Audrey Mitchell"
date: "7/21/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(NMF)
library(MutationalPatterns)
library(tidyverse)
library(ggrepel)
library(ROCR)
library(gridExtra)
source("bayes_function.R")
source("get_classification_df.R")
source("simulation.R")
sessionInfo()
```

@@

```{r}
set.seed()
#Create Signature 4 Sample
sig4.500 <- create_signature_sample_vector(signature.4.mat, 500)
sig4.profile <- vector_to_matrix(sig4.500)

@@

plot(MMR.perf, print.cutoffs.at=0.5, text.adj=c(-0.2,1.7),lty = 3) #ROC
plot(tob.perf, print.cutoffs.at=0.5, text.adj=c(-0.2,1.7), 
     add = TRUE, lty = 2)
abline(a=0, b= 1)
legend("bottomright", c("SBS4", "SBS6"),
       lty = 2:3)

@@

<!-- # Mutational load performance characteristics -->

<!-- ## Mutational load predictions -->

<!-- ```{r} -->
<!-- step_load = seq(50, 1000, by = 50) -->
<!-- MMR.probabilities <- vector(mode = "list", length = length(step)) -->
<!-- MMR.truth <- vector(mode = "list", length = length(step)) -->

<!-- for (x in 1:length(step)){ -->
<!--   sample.ffpe <- create_signature_sample_vector(ffpe.sig, step[x]/2) -->
<!--   ffpe.truth <- rep("FFPE", step[x]/2) -->
<!--   sample.sig6 <- create_signature_sample_vector(cosmic.sig6, step[x]/2) -->
<!--   sig6.truth <- rep("MMR", step[x]/2) -->
<!--   test <- get_classification_df(list(sample.sig6, sample.ffpe), c("MMR","FFPE"), -->
<!--                                 list(cosmic.sig6, ffpe.sig)) -->
<!--   classification <- test %>% -->
<!--     mutate(trueBinary = ifelse(truth == "MMR",1,0)) -->

<!--   MMR.probabilities[[x]] <- classification$MMR -->
<!--   MMR.truth[[x]] <- classification$trueBinary -->
<!-- } -->
<!-- ``` -->

<!-- ```{r} -->
<!-- tob.probabilities <- vector(mode = "list", length = length(step)) -->
<!-- tob.truth <- vector(mode = "list", length = length(step)) -->

<!-- for (x in 1:length(step)){ -->
<!--   sample.ffpe <- create_signature_sample_vector(ffpe.sig, step[x]/2) -->
<!--   ffpe.truth <- rep("FFPE", step[x]/2) -->
<!--   sample.sig4 <- create_signature_sample_vector(cosmic.sig4, step[x]/2) -->
<!--   sig4.truth <- rep("tob", step[x]/2) -->
<!--   test <- get_classification_df(list(sample.sig4, sample.ffpe), c("Tobacco","FFPE"), -->
<!--                                 list(cosmic.sig4, ffpe.sig)) -->
<!--   classification <- test %>% -->
<!--     mutate(trueBinary = ifelse(truth == "Tobacco",1,0)) -->

<!--   tob.probabilities[[x]] <- classification$Tobacco -->
<!--   tob.truth[[x]] <- classification$trueBinary -->
<!-- } -->
<!-- ``` -->

<!-- ```{r} -->
<!-- load.MMR <- prediction(MMR.probabilities, MMR.truth) -->
<!-- load.tob <- prediction(tob.probabilities, tob.truth) -->
<!-- ``` -->

<!-- ## Sensitivity -->

<!-- ```{r} -->
<!-- load.sens.MMR.vec = evaluate_perf(100, length(step_load), load.MMR, "sens") -->
<!-- load.sens.tob.vec = evaluate_perf(100, length(step_load), load.tob, "sens") -->
<!-- ``` -->

<!-- ```{r} -->
<!-- #plot(step, load.sens.MMR.vec, ylim = c(0,1)) -->
<!-- sensitivity = append(load.sens.MMR.vec, load.sens.tob.vec) -->
<!-- signature.sens = append(rep("MMR", length(load.sens.MMR.vec)), -->
<!--                         rep("Tobacco", length(load.sens.tob.vec))) -->
<!-- dilution = append(step, step) -->
<!-- sens.df <- data.frame(dilution, sensitivity, signature.sens) -->

<!-- ggplot(data = sens.df, mapping = aes(x = dilution,  -->
<!--                                      y = sensitivity,  -->
<!--                                      color = signature.sens)) + -->
<!--   geom_point() + -->
<!--   geom_smooth() + -->
<!--   labs(title = "Sensitivity as a function of mutational load", -->
<!--        x = "Number of mutations in each sample", -->
<!--        y = "Sensitivity value", -->
<!--        color = "True signal") + -->
<!--   coord_cartesian(ylim = c(0,1)) -->
<!-- ``` -->

<!-- ## Specificity -->

<!-- ```{r} -->
<!-- load.spec.MMR.vec = evaluate_perf(100, length(step.load), load.MMR, "spec") -->
<!-- load.spec.tob.vec = evaluate_perf(100, length(step.load), load.tob, "spec") -->
<!-- ``` -->

<!-- ```{r} -->
<!-- #plot(step, load.spec.MMR.vec, ylim = c(0,1)) -->

<!-- specificity = append(load.spec.MMR.vec, load.spec.tob.vec) -->
<!-- signature.spec = append(rep("MMR", length(load.spec.MMR.vec)), -->
<!--                         rep("Tobacco", length(load.spec.tob.vec))) -->
<!-- dilution = append(step, step) -->
<!-- spec.df <- data.frame(dilution, specificity, signature.spec) -->

<!-- ggplot(data = spec.df, mapping = aes(x = dilution,  -->
<!--                                      y = specificity,  -->
<!--                                      color = signature.spec)) + -->
<!--   geom_point() + -->
<!--   geom_smooth() + -->
<!--   labs(title = "Specificity as a function of mutational load", -->
<!--        x = "Number of mutations in each sample", -->
<!--        y = "Specificity value", -->
<!--        color = "True signal") + -->
<!--   coord_cartesian(ylim = c(0,1)) -->
<!-- ``` -->
